### 2022-05-07 paper/ase22/CM/coverage.tex
writing

Fig. \ref{fig:coverage} shows the coverage results of the generated
test samples, where the red line represents \tool and the black line
represents \Cklst.  Each column in Fig. \ref{fig:coverage} represent
the results for one NLP model, the first row is the \textit{BoundCov}
results and the second row is the \textit{SActCov} results.  From the
results, we make two observations observations. First, for \emph{all}
experimental settings (\eg NLP model, coverage metric), \tool achieves
high coverage than \Cklst. Recall that a higher coverage implies the
test case in the test suite is more diverse and rarely to have a
statistical distribution similar to the model training data. As a
result, a test suite with greater coverage complements the model
training data distribution (\ie hold-out testing data) better.  The
experimental results confirm that \tool can generate more diverse test
cases to complement the hold-out testing data for testing NLP models.
\sw{What does the growth trend in each figure indicate?} \sw{Does the
  absolute numbers or relative difference of the two lines on y axis
  mean anything concrete? E.g., how significant is the improvement in
  diversity?}

>>>>

Next, Fig. \ref{fig:coverage} shows the coverage results of the
generated test samples and reliability of the former evaluation
results. In the figure, the red line represents \tool and the black
line represents \Cklst. Each column in Fig. \ref{fig:coverage}
represent the results for one NLP model, the first row is the
\textit{BoundCov} results and the second row is the \textit{SActCov}
results.  From the results, we make three observations
observations. \TODO{First, as the number of test cases increases, the
  test suite can achieve better coverage. Such observation is
  intuitive. However, generating a more extensive test suite is not
  easy, particularly for \Cklst, which is a manually template-based
  approach.}  Second, for \emph{all} experimental settings (\eg NLP
model, coverage metric), \tool achieves high coverage than
\Cklst. Recall that a higher coverage implies the test case in the
test suite is more diverse and rarely to have a statistical
distribution similar to the model training data. As a result, a test
suite with greater coverage complements the model training data
distribution (\ie hold-out testing data) better.  \TODO{For example,
  for the first NLP model under test, \tool can achieve a higher
  coverage than \Cklst with only half test cases.}  Such experimental
results confirm that \tool can generate more diverse test cases to
complement the hold-out testing data for testing NLP models.  \sw{What
  does the growth trend in each figure indicate?} \sw{Does the
  absolute numbers or relative difference of the two lines on y axis
  mean anything concrete? E.g., how significant is the improvement in
  diversity?}

### 2022-05-07 paper/ase22/approach.tex
edit exp & table
writing

Algorithm \ref{alg:diff} shows how masks are identified for each seed
\sent.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) from the Penn Treebank corpus
dataset \cite{} as inputs.  The reference CFG is learned from a large
dataset \cite{} that is representative of the distribution of
real-world language usage.  The algorithm identifies the discrepancy
between the seed syntax and the reference grammar to decide how a seed
can be expanded.
%This phase builds \pcfg from the reference corpus. \cfg
%is constructed by parsing \sents in the corpus and extracting
%\prodrs. In addition, the probability of \cfg is estimated by
%its frequency over corpus. The output of this phase is the constructed
%\pcfg, and it is compared with seed parse trees. For our
%implementation, we build the \pcfg from the Penn Treebank corpus dataset.

@@

%Given the seed parse tree and reference \pcfg, production
%differentiation phase suggests structural expansion candidates on the
%seed input. this phase aims to analyze which structural components and
%where they can be added into the seed structure for its expansion. To
%do so, we explore reference \prodrs comparing it with each \prodr used
%in seed input. This results in the phase described in
%Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
%inputs ($seed\_prod$), it searches production rules in reference
%($ref\_prod$) which it has same non-terminal on the \lhs
%($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
%production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
%assume that the reference \cfg is built from real world data
%distribution, the elements in the complement set ($ref\_prod.rhs -
%seed\_prod.rhs$) become an expansion candidate which can be expanded
%from the $seed\_prod.rhs$ found in real world. In addition, the
%measure of how consistent the production rule is with the given seed
%structure is given in its probability of the reference production rule
%($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
%expansion candidate consists of terminal or nonterminal symbols. When
%there is a phrase-level or clause-level nonterminal symbol, \eg noun
%phrase, it needs to be expanded and replaced with word-level
%nonterminal or terminal symbols to generate the expansion
%candidate. The number of feasible replacement is unbounded because of
%its high degree of freedom. Therefore, in this work, we focus on the
%expansion candidate with only the word-level nonterminal or terminal
%symbols for the effectiveness of \Model. Lastly, the expanded
%component is replaced with the mask token for the next phase. The
%example of the expansion is illustrated in
%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
%reference, and ``NP->[DT,NNS]'' is identified as its expansion
%candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
%``NP->[DT]''. the component of NNS is replaced with mask token in
%\sent-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
%the next phase.

@@

In this work, out of the BERT suggested words, we randomly selects
words that matches their PoS tag of the expanded symbol in the parse
tree. The words that meets the second and third criteria are finally
employed for the expanded \sents.
% Our goal for generating the expanded \sents is to use them for
% evaluating the \sa models on the associated \lc in addition to the
% seed \sent. It is only achieved when the expanded \sents are also met
% with the same search rules for the \lc. For LC1 as an example, the
% expanded \sent must still conform to the specification of the seed's
% \lc specification. Therefore, the expanded \sents are required to be
% short and to only have \neu adjectives and \nns.
% \sw{Say why we use
%   the third criteria only for LC1 and LC2.}  \jl{I added the
%   explanation}

@@

%% \paragraph{Running example.} \jl{I dont think we need this
%%   subsection of \sent selection it is already explained at the
%%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}

>>>>

Algorithm \ref{alg:diff} shows how masks are identified for each seed
\sent.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) from the Penn Treebank corpus
dataset \cite{mitchell1993treebank} as inputs.  The reference CFG is
learned from a large dataset \cite{nltkTreebankCorporaWebPage} that is
representative of the distribution of real-world language usage.  The
algorithm identifies the discrepancy between the seed syntax and the
reference grammar to decide how a seed can be expanded.
%This phase builds \pcfg from the reference corpus. \cfg
%is constructed by parsing \sents in the corpus and extracting
%\prodrs. In addition, the probability of \cfg is estimated by
%its frequency over corpus. The output of this phase is the constructed
%\pcfg, and it is compared with seed parse trees. For our
%implementation, we build the \pcfg from the Penn Treebank corpus dataset.

@@

%Given the seed parse tree and reference \pcfg, production
%differentiation phase suggests structural expansion candidates on the
%seed input. this phase aims to analyze which structural components
%and where they can be added into the seed structure for its
%expansion. To do so, we explore reference \prodrs comparing it with
%each \prodr used in seed input. This results in the phase described
%in Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
%inputs ($seed\_prod$), it searches production rules in reference
%($ref\_prod$) which it has same non-terminal on the \lhs
%($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
%production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
%assume that the reference \cfg is built from real world data
%distribution, the elements in the complement set ($ref\_prod.rhs -
%seed\_prod.rhs$) become an expansion candidate which can be expanded
%from the $seed\_prod.rhs$ found in real world. In addition, the
%measure of how consistent the production rule is with the given seed
%structure is given in its probability of the reference production
%rule ($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
%expansion candidate consists of terminal or nonterminal symbols. When
%there is a phrase-level or clause-level nonterminal symbol, \eg noun
%phrase, it needs to be expanded and replaced with word-level
%nonterminal or terminal symbols to generate the expansion
%candidate. The number of feasible replacement is unbounded because of
%its high degree of freedom. Therefore, in this work, we focus on the
%expansion candidate with only the word-level nonterminal or terminal
%symbols for the effectiveness of \Model. Lastly, the expanded
%component is replaced with the mask token for the next phase. The
%example of the expansion is illustrated in
%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into reference,
%and ``NP->[DT,NNS]'' is identified as its expansion candidate since
%the \rhs of ``NP->[DT,NNS]'' is superset of that of ``NP->[DT]''. the
%component of NNS is replaced with mask token in
%\sent-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
%the next phase.

@@

In this work, out of the BERT suggested words, we randomly selects
words that matches their PoS tag of the expanded symbol in the parse
tree. The words that meets the second and third criteria are finally
employed for the expanded \sents.
% Our goal for generating the expanded \sents is to use them for
% evaluating the \sa models on the associated \lc in addition to the
% seed \sent. It is only achieved when the expanded \sents are also
% met with the same search rules for the \lc. For LC1 as an example,
% the expanded \sent must still conform to the specification of the
% seed's \lc specification. Therefore, the expanded \sents are
% required to be short and to only have \neu adjectives and \nns.
% \sw{Say why we use the third criteria only for LC1 and LC2.}  \jl{I
% added the explanation}

@@

% \paragraph{Running example.} \jl{I dont think we need this
%   subsection of \sent selection it is already explained at the
%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}

### 2022-05-07 paper/ase22/experiment.tex
writing

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool. The \Sstt is a
corpus of movie review, and it consists of 11,855 single sentences
with its sentiment score. As original dataset suggests, we split the
score range into [0, 0.4], (0.4, 0.6] and (0.6, 0.8] for assigning
    negative, neutral and positive labels respectively.
%% \TODO{introduce details about each model}

@@

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus. We
expect \tool can generate a more diverse test suite than \Cklst. To
measure diversity, we follow the approach presented by Ma et
al. \cite{ma2018deepgauge}, where the authors measure the coverage of
NLP model intermediate states as corner-case neurons.  Because the
matrix computation of intermediate states impacts NLP model
decision-making, a test suite that covers a greater number of
intermediate states can represent more NLP model decision-making,
making it more diverse.  Specifically, we used two coverage metrics in
existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
(BoundCov) and \textit{strong activation coverage} (SActCov), as our
metrics to evaluate the test suite diversity.  \TODO{It is worth
  noting that a test sample with a statistical distribution similar to
  the training data would rarely be found in the corner case
  region. As a result, covering a larger corner case region means that
  the test suite is more likely to be buggy.}

>>>>

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool. The \Sstt is a
corpus of movie review, and it consists of 11,855 single sentences
with its sentiment score. As original dataset suggests, we split the
score range into [0, 0.4], (0.4, 0.6] and (0.6, 0.8] for assigning
    negative, neutral and positive labels respectively. In addition,
    we use \Swn as word sentiment
    dataset~\cite{baccianella2010sentiwordnet}. \Swn is a publicly
    available English sentiment lexicons.  It provides lexical
    sentiment scores and the sentiment word labels are categorized by
    implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
%% \TODO{introduce details about each model}

@@

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus.  We
expect \tool can generate a more diverse test suite than \Cklst, and
achieve more probable evaluation results. We first evaluate the three
\sa models by testing them on the test cases that \tool
generates. Next, to measure diversity, we follow the approach
presented by Ma et al. \cite{ma2018deepgauge}, where the authors
measure the coverage of NLP model intermediate states as corner-case
neurons.  Because the matrix computation of intermediate states
impacts NLP model decision-making, a test suite that covers a greater
number of intermediate states can represent more NLP model
decision-making, making it more diverse.  Specifically, we used two
coverage metrics in existing work \cite{ma2018deepgauge},
\textit{boundary coverage} (BoundCov) and \textit{strong activation
  coverage} (SActCov), as our metrics to evaluate the test suite
diversity.  \TODO{It is worth noting that a test sample with a
  statistical distribution similar to the training data would rarely
  be found in the corner case region. As a result, covering a larger
  corner case region means that the test suite is more likely to be
  buggy.}

### 2022-05-07 paper/ase22/result.tex
writing

\InputWithSpace{tables/manual-study-table}
\InputWithSpace{tables/test-results-table}

\subsection{RQ1: \tool Sentiment Label Consistency}
Table~\ref{table:ManualStudy} shows the statistics of scores collected
from the manual study of \tool. First column represents type of test
case. The number of test cases used for the study is represented in
second column. Label consistency score and \lc relevancy score defined
at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
remaining columns. First, it is shown that high label consistency
score over 0.8. It means that \tool generates test oracles consistent
to human understanding. It is also observed that there is no
difference of the scores between seed and expanded sentences. The
observation implies that the expansion method in \tool preserves
sentiment of expanded sentences as its seed, and provides its
reliability. These observations answer RQ1 and conclude that \tool
generates test case with high consistency between test sentence and
its oracle.

\subsection{RQ2: Correctness of Linguistic Capability Categorization}
The result in table~\ref{table:ManualStudy} also shows that \tool
achieves high order of agreement with human assessment on \lc
relevancy. In parallel, it is observed that the expanded sentences
generated from \tool also have same level of \lc
relevancy. Accordingly, we answer the RQ2 by concluding that
\tool generates \lc relevant test cases with the agreement with human.

\jl{The following needs to be in RQ2 result section after simin
  completes RQ2 result section} Table~\ref{table:TestResult} shows
results of evaluation of three \sa models. First column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by evaluating the \sa models on the seed
and expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed.  From
the table, we can observe that LC3 has no expanded sentences from its
seeds. It means that the 50 seeds selected in this experiment does not
provide any validated expansions. It is because the randomness of
selection of 50 seeds determines the number of validated
expansions. we expect that more selection of seeds increases the
probability of availability of their expansion. In addition, LC1 and
LC5 obtains 19 and 26 seeds respectively. It represents that \tool
finds and generates their seeds lower than the target number of seeds,
which is 50 in this experiment. In this case, use of larger search
dataset increases the amount of seeds for the \lcs. Finally, we find
that there are number of a number of failed expanded test cases succeeded
before the expansion (pass on seed, but fail on its expanded test
cases). This shows that phase of syntax-based sentence expansion in
\tool captures failure-inducing expansion given a seed. It finally
shows usefulness of \tool since the different test results between seed
and expanded cases provide accurate guidance for debugging model.

\subsection{RQ3: Test Suite Diversity}
\input{CM/coverage}

>>>>

\InputWithSpace{tables/manual-study-table}
\InputWithSpace{tables/test-results-table}
\subsection{RQ1: \tool Sentiment Label Consistency}
Table~\ref{table:ManualStudy} shows results of our manual study. The
first column represents type of test case. The number of test cases
used for the study is represented in second column. The label
consistency score defined in equation~\ref{metric:srel} is shown in
column 3.

We observe that \emph{\tool generates test cases that consistently
  label their sentiment correctly.}  Column 3 shows that the label
consistency scores are 0.83 and 0.84 for the seed and expanded
sentences, respectively. We can observe that the scores are not same
as maximum scores meaning that there are inconsistency on labels
between \tool and subjects. The cuases of inconsistency in the scores
are two following: First, complicated sentence leads subjects to
misunderstand its meaning. Second, phrase in a sentence introduces its
multiple interpretations to understand its sentiment. For example, the
word ``easy'' could be interpreted as both compliment and back-handed
insult.  This means that \tool generates test oracles consistent with
human understanding most of the time. It is observed that there is
little difference of the scores between the seed and expanded
sentences. This implies that the syntax-based sentence expansion in
\tool preserves the sentiment as its seed.
%% \sw{What are
%%   the causes of inconsistency? Looks like the main source of
%%   inconsistency comes from seed generation? Any insights on how it
%%   happened (e.g., issue with original labels, search rules, or
%%   templates?}

\subsection{RQ2: Correctness of Linguistic Capability Categorization}
The \lc relevancy score defined in~\ref{metric:lcrel} is shown in
column 4 of Table \ref{table:ManualStudy}. The result shows that
\emph{\tool generates test cases that are correctly categorized to the
  corresponding linguistic capabilities most of the time.}  The \lc
relevancy scores for the seed and expanded sentences are both 0.9,
achieving high order of agreement with human assessment. The fact that
the expanded sentences generated by \tool also have same level of \lc
relevancy as the seed sentences shows that the syntax-based sentence
expansion retains the linguistic capabilities.
%% \sw{Source of incorrect
%% categorization of linguistic capabilities?}

\subsection{RQ3: Test Suite Diversity}

We first show evaluation results of three \sa models via
table~\ref{table:TestResult}. In the table, first column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by evaluating the \sa models on the seed
and expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed.  From
the table, we can observe that LC3 has no expanded sentences from its
seeds. It means that the 50 seeds selected in this experiment does not
provide any validated expansions. It is because the randomness of
selection of 50 seeds determines the number of validated
expansions. we expect that more selection of seeds increases the
probability of availability of their expansion. In addition, LC1 and
LC5 obtains 19 and 26 seeds respectively. It represents that \tool
finds and generates their seeds lower than the target number of seeds,
which is 50 in this experiment. In this case, use of larger search
dataset increases the amount of seeds for the \lcs. From the table, it
is found that all three models achieves better performance on LC9 and
LC2 while they obatains high failure rates on other \lcs. Finally, we
find that there are number of a number of failed expanded test cases
succeeded before the expansion (pass on seed, but fail on its expanded
test cases). This shows that phase of syntax-based sentence expansion
in \tool captures failure-inducing expansion given a seed. It finally
shows usefulness of \tool since the different test results between
seed and expanded cases provide accurate guidance for debugging model.

\input{CM/coverage}
